Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-09-05 paper.tex
Add files via upload

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aCR.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aCR.eps}
   \end{center}
\end{minipage}
\caption{Sensitivity of the radio emission in the Coma cluster to critical
  parameters. The left-hand panels show the radio surface brightness
  profiles. We compare profiles at 352~MHz \citep[blue
    crosses,][]{brown11} to predicted emission from Fermi-II
  reaccelerated CR electrons populations (black lines). The right-hand
  panels show radio synchrotron spectra. The green crosses are
  compiled from observations \citep{2010PhDT.......259P}, while the
  black lines show predicted spectra. The upper panels show the sensitivity to the level of
  turbulence ($X_\rmn{tu}$), the middle panels show the impact of
  different turbulent profiles ($\alpha_\rmn{tu}$), and the lower
  panels show the dependence on spatial distributions of initial and
  injected CRs ($\alpha_\rmn{CR,spat}$). We adopt the following
  fiducial values for our model, $X_\rmn{tu}=0.2$,
  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$ and vary each
  parameter separately in each row of panels. We find that the radio
  emission is most sensitive to the level of turbulence. The abundance of CR seeds, and the spatial distribution of CRs and turbulence play second-order effects.}
  \label{fig:param_comp}
\end{figure*}

@@

It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation \ref{eqn:ratios_CR_damp}). We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.  They are remarkably revealing. In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population. This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.

@@

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{tcltD.prof.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{tcltD.spec.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{tcltD.prof.comp.KrTTDth.aI0.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{tcltD.spec.comp.KrTTDth.aI0.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{tcltD.prof.comp.KrTTDth.aCR.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{tcltD.spec.comp.KrTTDth.aCR.eps}
   \end{center}
\end{minipage}
\caption{Sensitivity of radio emission in Coma cluster to critical
  parameters. For details see caption in
  Figure~\ref{fig:param_comp}. For simplicity, we assume that the
  duration of reacceleration $\tau_{cl}=\tau_{\rm D}$, where $\tau_{\rm
    D}$ is the acceleration time of particles due to turbulence. In
  this scenario the radio profiles are mainly determined from the CRs,
  while the turbulence has a minor impact. Interestingly, flat CR
  profiles similar to those produced through CR streaming are needed in
  order to reproduce the radio profiles.}
  \label{fig:param_comp_tcl_tD}
\end{figure*}

>>>>

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aCR.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aCR.eps}
   \end{center}
\end{minipage}
\caption{Sensitivity of the radio emission in the Coma cluster to critical
  parameters. The left-hand panels show the radio surface brightness
  profiles. We compare profiles at 352~MHz \citep[blue
    crosses,][]{brown11} to predicted emission from Fermi-II
  reaccelerated CR electrons populations (black lines). The right-hand
  panels show radio synchrotron spectra. The green crosses are
  compiled from observations \citep{2010PhDT.......259P}, while the
  black lines show predicted spectra. The upper panels show the sensitivity to the level of
  turbulence ($X_\rmn{tu}$), the middle panels show the impact of
  different turbulent profiles ($\alpha_\rmn{tu}$), and the lower
  panels show the dependence on spatial distributions of initial and
  injected CRs ($\alpha_\rmn{CR,spat}$). We adopt the following
  fiducial values for our model (solid lines), $X_\rmn{tu}=0.2$,
  $\alpha_\rmn{tu}=0.8$, and $\alpha_\rmn{CR,spat}=1.0$ and vary each
  parameter separately in each row of panels. We find that the radio
  emission is most sensitive to the level of turbulence. The abundance of CR seeds, and the spatial distribution of CRs and turbulence play second-order effects.}
  \label{fig:param_comp}
\end{figure*}

@@

\sout{It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation \ref{eqn:ratios_CR_damp}). We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values, but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm cl}=\tau_{\rm D}$.  They are remarkably revealing. In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population. This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.}
\C{It is interesting to reconsider surface brightness and spectral profiles if indeed $\tau_{\rm D} \sim \tau_{\rm cl}$, for the reasons mentioned above (e.g., equation~\ref{eqn:ratios_CR_damp}). We show the results of adopting such an ansatz in Figure~\ref{fig:param_comp_tcl_tD}, where, similar to Figure~\ref{fig:param_comp}, we vary $X_{\rm tu}, \alpha_{\rm tu}, \alpha_{\rm CR, spat}$ about fiducial values \footnote{When $\tau_{\rm D} \sim \tau_{\rm cl}$ is adopted, the radial behavior of $\tau_{\rm cl}$ is also changed. Since $\tau_{\rm D}$ decreases with radius (see e.g. Figure~\ref{fig:tauD}), $\tau_{\rm cl}$ has to decrease with the same amount which results in a steeper radio profile. To compensate for this in Figure~\ref{fig:param_comp_tcl_tD}, we change $\alpha_{\rm CR, spat}\rightarrow0.5$ and decrease the relative CR-to-thermal energy within the virial radius with a factor five to 0.06 per cent.} , but this time we do not adopt a fixed $\tau_{\rm cl}$ but set $\tau_{\rm D} = 1/4 \,\tau_{\rm cl}$. They are remarkably revealing. In this case, one is much less sensitive to the properties of the turbulence, and more sensitive to the details of the CR seed population.  This gives hope to the possibility that one could effectively marginalise over the very uncertain properties of turbulence at larger scales in merging clusters (which are unlikely to be more precisely constrained observationally in the near future) to learn something about the underlying CR population.}

@@

\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio profiles}\\
     \includegraphics[width=\columnwidth]{figure7_prof.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{radio spectra}\\
     \includegraphics[width=\columnwidth]{figure7_spec.eps}
   \end{center}
\end{minipage}

\caption{\C{Sensitivity of radio emission in Coma cluster to critical
    parameters. For details see caption in
    Figure~\ref{fig:param_comp}. For the fiducial model we adopt a
    slightly flatter distribution of CRs ($\alpha_{\rm CR, spat}=0.5$)
    and a factor five lower CR-to-thermal energy than in previous
    figure. We assume that the duration of reacceleration
    $\tau_{cl}=2.5\,\tau_{\rm D}$, where $\tau_{\rm D}$ is the
    acceleration time of particles due to turbulence. In this scenario
    the radio profiles are mainly determined from the CRs, while the
    turbulence has a minor impact. In the bottom two panels we vary
    $\tau_{cl}=\tau_{\rm D}$, which mainly changes the normalization
    of the CR distribution and not the shape or radial
    dependence. Interestingly, flat CR profiles similar to those
    produced through CR streaming are needed in order to reproduce the
    radio profiles.}}
  \label{fig:param_comp_tcl_tD}
\end{figure*}
